Priors for Latent Hawkes

### 2020-06-22 output_scripts/New_Priors.Rmd
improved examples

```{r}
current_cohort <- 2
print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

```
We can similarly look at the original fits (with and without considering the windows with 
no events).

@@

```{r}
p1 <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Priors")

@@

current_cohort <- 2
print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

@@

p1_new
```
We can compare this to the previous fit.

@@

```{r, fig.height=10}
ggpubr::ggarrange(p1,p1_new,nrow=2)
```

>>>>

```{r}
current_cohort <- 1
print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

We can similarly look at the original fits (with and without considering the windows with 
no events).

@@

```{r}
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))

p1 <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Priors")

@@

print(current_cohort)
load(paste(data_path,cohort_names[current_cohort],
         "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
         ".RData",sep=''))
rstan::stan_hist(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) +
  ggtitle("New Priors")
rstan::traceplot(fit_cohort_mmhp,
               pars = c("lambda0","lambda1","w_lambda",
                        "eta_1","eta_2","eta_3","beta")) + 
  ggtitle("New Priors")

@@

p1_new
```

We can compare this to the previous fit.

@@

```{r, fig.height=10}
print(current_cohort)
ggpubr::ggarrange(p1,p1_new,nrow=2)
```

We can repeat this for another cohort.

```{r, fig.height=10}
current_cohort <- 2

print(current_cohort)
data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_prior//"
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
p1 <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Prior")

data_path <- "C:/Users/owenw/Google Drive/Tian/Current_Projects/MMHP_Latent/output_p1/"
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
p1_new <-rstan::traceplot(fit_cohort_mmhp,
                 pars = c("f")) + 
  ggtitle("New Prior, lower bound lambda0")

ggpubr::ggarrange(p1,p1_new,nrow=2)
